Matching bullets

### 2015-11-18 imaging-paper.Rnw
image name
moving images

Each fired bullet is provided in form of a set of six x3p files, where each file is a surface scan between adjacent grooves on the bullet, called a ``land". An example of plotting one of these lands is given in Figures~\ref{fig:sidex3p} and~\ref{fig:topx3p}, which show side and top profiles of the land respectively.

\begin{figure}
  \centering
    \includegraphics[width=\linewidth]{images/sidex3p.png}
  \caption{An example of a scan of a bullet land, viewed from the side.}
  \label{fig:sidex3p}
\end{figure}

\begin{figure}
  \centering
    \includegraphics[width=\linewidth]{images/topx3p.png}
  \caption{An example of a scan of a bullet land, viewed from the top.}
  \label{fig:topx3p}
\end{figure}

@@

<<fixedX, dependson='data', echo=FALSE, warning=FALSE, message=FALSE, fig.width=6, out.width='\\linewidth', fig.pos='t!', fig.cap='Side profile of the height values of a bullet land across fixed x values. Note that the global features dominate any deviations, which would correspond to markings.'>>=
library(RColorBrewer)
library(ggplot2)
library(dplyr)
library(x3pr)
library(x3prplus)

@@

\begin{figure}
\includegraphics[width=\columnwidth]{images/match-rgl.png}
\caption{\label{fig:manualmatch}\hh{Different view of the manually adjusted side-by-side comparison of two lands from different bullets.}}
\end{figure}

>>>>

\begin{figure}[hbtp]
  \centering
    \subfloat[View from the side.\label{fig:sidex3p}]{%
      \includegraphics[width=\linewidth]{images/sidex3p.png}
    }
    \hfill
    \subfloat[View from the top.\label{fig:topx3p}]{%
    \includegraphics[width=\linewidth]{images/topx3p.png}
    }
\caption{An example of a scan of a bullet land.}
\end{figure}
Each fired bullet is provided in form of a set of six x3p files, where each file is a surface scan between adjacent grooves on the bullet, called a ``land". An example of plotting one of these lands is given in Figures~\ref{fig:sidex3p} and~\ref{fig:topx3p}, which show side and top profiles of the land respectively.

@@

<<fixedX, dependson='data', echo=FALSE, warning=FALSE, message=FALSE, fig.height=2.5, fig.width=6, out.width='\\linewidth', fig.pos='t!', fig.cap='Side profile of the height values of a bullet land across fixed x values. Note that the global features dominate any deviations, which would correspond to markings.'>>=
library(RColorBrewer)
library(ggplot2)
library(dplyr)
library(x3pr)
library(x3prplus)

@@

\begin{figure}
\includegraphics[width=\columnwidth]{images/matchup-rgl.png}
\caption{\label{fig:manualmatch}\hh{Different view of the manually adjusted side-by-side comparison of two lands from different bullets.}}
\end{figure}
